Supplementary Materials

### 2018-12-03 paper/paper.tex
Updated authors
Performed PCA from 1 through 12 dimensions and plotted graph of performance

\author[1]{Rahul Yedida}
\author[1]{Snehanshu Saha}
\affil[1]{Department of Computer Science \& Engineering, PESIT South Campus}

@@

\subsection{Cluster Analysis}
We next sought to cluster the points, as a first step towards identifying ``prolific" authors. Because finding the number of clusters in such high dimensional data is difficult, we chose to use two different algorithms--DBSCAN (Density-Based Spatial Clustering of Applications with Noise)\cite{ester1996density} and mean-shift clustering \cite{comaniciu2002mean} from Python's sklearn package \cite{scikit-learn}. We picked two subsets of the data to perform this analysis on--the first was the set of variables that were highly correlated with \textit{v4} (denote this subset as $S_1$)--we chose these because it had an especially high number of correlated variables--and the second was the subset discussed in the previous subsection (which we shall denote as $S_2$.

>>>>

\author[1]{Rahul Yedida}
\author[2]{Adel Aladwani}
\author[1]{Snehanshu Saha}
\affil[1]{Department of Computer Science \& Engineering, PES University}
\affil[2]{Department of Information Systems, Kuwait University}

@@

	\subsection{Cluster Analysis}
	We next sought to cluster the points, as a first step towards identifying ``prolific" authors. Because finding the number of clusters in such high dimensional data is difficult, we chose to use two different algorithms--DBSCAN (Density-Based Spatial Clustering of Applications with Noise)\cite{ester1996density} and mean-shift clustering \cite{comaniciu2002mean} from Python's sklearn package \cite{scikit-learn}. We picked two subsets of the data to perform this analysis on--the first was the set of variables that were highly correlated with \textit{v4} (denote this subset as $S_1$)--we chose these because it had an especially high number of correlated variables--and the second was the subset discussed in the previous subsection (which we shall denote as $S_2$. We also performed the clustering analysis with DBSCAN using PCA instead of manually picking features. The results of that are discussed in the Supplementary Materials.

### 2018-12-03 paper/supp.tex
Minor corrections to paper
Performed PCA from 1 through 12 dimensions and plotted graph of performance

\begin{tabular}{|c|c|}
\hline 
\textbf{Variable} & \textbf{Meaning} \\ 
\hline 
v1 & Number of papers \\ 
\hline 
v2 & Total citations \\ 
\hline 
v3 & Production years \\ 
\hline 
v4 & Cites per year (?) \\ 
\hline 
v5 & Cites per paper (?) \\ 
\hline 
v6 & Cites per author (?) \\ 
\hline 
v7 & Papers per author (?) \\ 
\hline 
v8 & Authors per paper (?) \\ 
\hline 
v9 & h-index \\ 
\hline 
v10 & g-index \\ 
\hline 
v11 & hc-index \\ 
\hline 
v12 & hl-index \\ 
\hline 
v13 & hl-norm \\ 
\hline 
v14 & AWCR \\ 
\hline 
v15 & AW index \\ 
\hline 
v16 & AWCR per annum \\ 
\hline 
v17 & e-index \\ 
\hline 
v18 & hm-index \\ 
\hline 
v19 & Cites author per year (?) \\ 
\hline 
v20 & CitesAuthorYearArticle \\ 
\hline 
v21 & Annual hl \\ 
\hline 
v22 & h Coverage \\ 
\hline 
v23 & g Coverage \\ 
\hline 
v24 & Star count \\ 
\hline 
v25 & Adjusted star count \\ 
\hline 
\end{tabular}
\begingroup
\captionof{table}{List of attributes in the data}
\endgroup

@@

\subsection{Analysis on $S_1$}
Figure 17 shows the analysis for $S_1$. The Silhouette score for DBSCAN here was 0.635.

@@

\subsection{Analysis on $S_2$}
Figure 18 shows the analysis for $S_2$. As noted in the paper, the Silhouette score for DBSCAN for this subset was 0.571. \\

>>>>

\begin{tabular}{|c|c|}
\hline 
\textbf{Variable} & \textbf{Meaning} \\ 
\hline 
v1 & Number of papers \\ 
\hline 
v2 & Total citations \\ 
\hline 
v3 & Production years \\ 
\hline 
v4 & Cites per year \\ 
\hline 
v5 & Cites per paper\\ 
\hline 
v6 & Cites per author\\ 
\hline 
v7 & PapersAuthor \\ 
\hline 
v8 & Authors per paper \\ 
\hline 
v9 & h-index \\ 
\hline 
v10 & g-index \\ 
\hline 
v11 & hc-index \\ 
\hline 
v12 & hl-index \\ 
\hline 
v13 & hl-norm \\ 
\hline 
v14 & AWCR \\ 
\hline 
v15 & AW index \\ 
\hline 
v16 & AWCR per author\\ 
\hline 
v17 & e-index \\ 
\hline 
v18 & hm-index \\ 
\hline 
v19 & CitesAuthorYear\\ 
\hline 
v20 & CitesAuthorYearArticle \\ 
\hline 
v21 & Annual hl \\ 
\hline 
v22 & h Coverage \\ 
\hline 
v23 & g Coverage \\ 
\hline 
v24 & Star count \\ 
\hline 
v25 & Adjusted star count \\ 
\hline 
\end{tabular}
\begingroup
\captionof{table}{List of attributes in the data}
\endgroup

@@

\subsection{PCA}
We performed a PCA before using DBSCAN. In all cases, we used the same method discussed in the paper to compute the value of \textit{eps}. We did this analysis for one through twelve dimensions. For number of dimensions greater than six, the performance stagnates at 0.571. We argue however, that the new dimensions obtained by PCA are less interpretable than simply using the original features, and the maximum difference between the performance of DBSCAN using our hand-picked features (0.571) and using PCA (0.644, n=2) was only 0.073. Figure 17 shows the results of using PCA to various numbers of dimensions.

\includegraphics[scale=0.7]{pca.png}
\begingroup
\captionof{figure}{Results of using PCA and then clustering with DBSCAN}
\endgroup

\subsection{Analysis on $S_1$}
Figure 18 shows the analysis for $S_1$. The Silhouette score for DBSCAN here was 0.635.

@@

\subsection{Analysis on $S_2$}
Figure 19 shows the analysis for $S_2$. As noted in the paper, the Silhouette score for DBSCAN for this subset was 0.571. \\
